---
title: "R Notebook"
output: github_document
---
Source files: https://iainpardoe.com/arm3e/software-info/r/


The [R plugin](https://www.jetbrains.com/help/pycharm/r-plugin-support.html) for IntelliJ-based IDEs provides
handy capabilities to work with the [R Markdown](https://www.jetbrains.com/help/pycharm/r-markdown.html) files.
To [add](https://www.jetbrains.com/help/pycharm/r-markdown.html#add-code-chunk) a new R chunk,
position the caret at any line or the code chunk, then click "+".

```{r}
require(dplyr)
```

The code chunk appears:
```{r}
setwd(getSrcDirectory(function(){})[1])
nba_fp <- "Applied_Regression_Modeling/data/arm3edata/nbasalary.csv"
nba_dat <- read.csv(nba_fp)
nba_dat %>% head()
```

```{r, fig.width=2, fig.height=1}
hist(nba_dat$Salary, main="", xlab="Price (sale price in $ thousands)")
```

```{r}
qqnorm(nba_dat$Salary)
qqline(nba_dat$Salary)
```

```{r}
mycars <- within(mtcars, { cyl <- ordered(cyl) })
mycars
```

Type any R code in the chunk, for example:
```{r}
mycars <- within(mtcars, { cyl <- ordered(cyl) })
mycars
```

Now, click the **Run** button on the chunk toolbar to [execute](https://www.jetbrains.com/help/pycharm/r-markdown.html#run-r-code) the chunk code. The result should be placed under the chunk.
Click the **Knit and Open Document** to build and preview an output.
